Incorporating individual variation in animal movement models

### 2021-02-12 movement_paper/2_11_explora.Rmd
Playing with the data

We can visualize the locations for each of the individuals tagged. The two separate groups represent the two locations considered: Yasuni Biosphere Reserve (upper left) and Tiputini Biodiversity Station (lower right).
```{r}
plot(aracari_data$y~aracari_data$x, 
     col = as.factor(aracari_data$animal_id), 
     pch = 16)
```

@@

  -   So, there is sampling error. A success/failure of capturing a signal every 15 minutes in those 4-6hours.

```{r}
aracari_ltraj
```

>>>>

We can visualize the locations for each of the individuals tagged. The two separate groups represent the two locations considered: Yasuni Biosphere Reserve (upper left) and Tiputini Biodiversity Station (lower right).
```{r}
plot(aracari_data$y~aracari_data$x, 
     col = as.factor(aracari_data$animal_id), 
     pch = 16)

```

@@

  -   So, there is sampling error. A success/failure of capturing a signal every 15 minutes in those 4-6hours.
  -   And, there are multiple tracking periods, each tracking period represented by a "burst"

```{r}
head(aracari_ltraj)

# Transform to a dataframe
aracari_df <- ld(aracari_ltraj)

aracari_df %>% drop_na(dt) %>% group_by(id) %>% distinct(burst) %>% tally()
```

```{r}

# I want to include family groups in that data set, just in case we want to use that later
# The social groups are as follows: (1, 3, 5), (7), (13, 19), (22), (28), and (49, 84).
# I've added another group for birds (29,30) which are Yasuni birds, with overlapping territories and I would assume they are a social group.
# All others are left as unknown.
aracari_df$id <- factor(aracari_df$id, levels = c(1, 3, 5, 7, 13, 19, 22, 28, 49, 84, 10, 17, 20, 21, 24, 29, 30, 9))
aracari_df %>%
  mutate(fam_g = ifelse(id %in% c(1,3,5), "f1",
                        ifelse(id == 7, "f2",
                               ifelse(id %in% c(13, 19), "f3",
                                      ifelse(id == 22, "f4",
                                             ifelse(id == 28, "f5",
                                                    ifelse(id %in% c(49,84),
                                                           "f6", 
                                                           ifelse(id %in% c(29, 30), "f7", "unknown")
                                             ))))))) -> aracari_df
```

```{r}
aracari_df %>% 
  group_by(id) %>% 
  distinct(burst) %>% 
  tally()

test <- aracari_df %>% 
   mutate(T_minutes = dt/60,
         #Bird_ID = id,
         mpm = dist/T_minutes,
         #R2n = lead(R2n)
         ) 
# %>%
#   filter(T_minutes != 0 & T_minutes %in% c(15, 30, 45, 60, 75, 90)) %>%
#   group_by(Bird_ID) %>%
#   add_tally()

path <- data.frame(aracari_ltraj[[1]], id = attr(aracari_ltraj[[1]], "id"))
for(i in 2:length(aracari_ltraj)){
  path <- rbind(path,
                data.frame(aracari_ltraj[[i]], id = attr(aracari_ltraj[[i]], "id")))
}

path$distperday <- path$dist/(path$dt/60/60/24)

# Aggregate to show mean distance per day for each turtle
path.summary <- aggregate(distperday~id, data = path, FUN = mean)
path.summary$sd <- aggregate(distperday~id, data = path, FUN = sd)$distperday

# Look at summmary dataframe
path.summary

# Make a graph to visualize data using ggplot

# Create limits used for error bars in graph
limits <- aes(ymax = path.summary$distperday + path.summary$sd, 
              ymin = path.summary$distperday - path.summary$sd)

# Make plot. Choose the dataframe (data) and aesthetics (aes; for the x and y)
ggplot(data = path.summary, aes(x = id, y = distperday, colour = id)) + 
  geom_point(size = 3) + # add points
  geom_errorbar(limits, width = 0.2) + # adds error bars
  labs(x = "Animal number", 
       y = "Mean distance travelled per day (m)" ) + # Axis labels
  theme_classic() + # Make plot black and white with no background grid
  theme(legend.position = "none")

```
